Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-14 doc/paper.tex
adds overview diagram

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage[review]{cvpr}      % To produce the REVIEW version
% \usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

@@

@@

>>>>

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage{cvpr}      % To produce the REVIEW version
% \usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

@@

\begin{figure}
    \centering
    %angle=-90,origin=c
    \includegraphics[width=8.5cm]{images/overview.pdf}
    \caption{Overview of }
    \label{fig:overview}
\end{figure}

@@

\section{Notes from Edwin}

\begin{itemize}
    \item Augmentations are random
    \item Explaining that it's a two step process, and thats how its different from prior work
    \item Goal is to see how 2D self-supervised features transferred to a 3D model work
    \item Mention that it uses a single image
\end{itemize}

\textbf{description:} Three steps. First step is pre-training, random combinations of a single image pixel contrast. Second stage is try to get 2D to 3D features match. Third is fine-tuning on 3D data.
